---
title: "Tempo Histograms"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(flexdashboard)
library (devtools)
library(tidyverse)
library(spotifyr)
library(knitr)
library(compmus)
library(dplyr)
library(plotly)
library(ggplot2)

Sys.setenv(SPOTIFY_CLIENT_ID = '9a3bb94792fb416eaaf55b08d63c0135')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '4d7c9421a08a4bad85d52c8b60485724')

access_token <- get_spotify_access_token()

kanye <- get_playlist_audio_features("", "7Ch9pFecrcS48qlvubVLJO")
kanye2 <- get_artist_audio_features('Kanye West')
hhs <- get_playlist_audio_features("", "4E55G0GYK0CuUWZ0IQiaoD")
jdilla <- get_playlist_audio_features("", "6eQuLy3XkE1ZZDKrV10CIK")
kanye <- get_playlist_audio_features("", "7Ch9pFecrcS48qlvubVLJO")
timbaland <- get_playlist_audio_features("", "56GlL98C6BFNZo3wjSNWYb")

```{r}

gotawoman <- get_tidy_audio_analysis("2xar08Fq5xra2KKZs5Bw9j")
golddigger <- get_tidy_audio_analysis("3QHPHLAkYV5cQBUYs6rowx")

```

-----------------------------------------------------------------------

# Kanye West Tempogram-Comparison of the original song and the sampled song 

#Ray Charles - I got a woman

```{r}

gotawoman %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

Column {data-width=350} {.tabset .tabset-fade}
-----------------------------------------------------------------------

#Kanye West - Gold Digger ft. Jamie Foxx 

```{r}

golddigger %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

Column {data-width=350} {.tabset .tabset-fade}
-----------------------------------------------------------------------
#Frequency of Tempo in songs by Knaye West and the samples he has used
```{r}
kanyetempo <- (kanye$tempo) 

hist(kanyetempo)

```

-----------------------------------------------------------------------
